Section Three

### 2020-10-04 new2020/sections/sec03.Rmd
texalpha in subfile

---
title: Section Three
header-includes:
   - \usepackage{cleveref}
   - \usepackage{booktabs}
   - \input{../symbols.tex}
---

@@

```{r overall_results,echo=FALSE,cache=TRUE,results="asis",dependson="load_results"}

res_overall <- eta_talk %>%
   filter(time_until_arrival > 0) %>%
   summarize(
      pf_rmse = sqrt(mean(pf_error^2)),
      pf_mae = mean(abs(pf_error)),
      pf_mape = mean(abs(pf_error / time_until_arrival)) * 100,
      pf_cicov = mean(pf_ci) * 100,
   #   pf_ci_width = mean(pf_upper - pf_lower),
   #   pf_ci_lower = quantile(pf_upper - pf_lower, 0.025),
   #   pf_ci_upper = quantile(pf_upper - pf_lower, 0.975),
      gtfs_rmse = sqrt(mean(gtfs_error^2)),
      gtfs_mae = mean(abs(gtfs_error)),
      gtfs_mape = mean(abs(gtfs_error / time_until_arrival)) * 100
   ) %>%
   pivot_longer(everything(),
      names_to = c("model", ".value"),
      names_pattern = "([a-z]*)_(.*)"
   ) %>%
   mutate(
      model = c("Particle filter", "Schedule-delay")
   ) %>%
   rename(
      " " = "model",
      "RMSE (s)" = "rmse",
      "MAE (s)" = "mae",
      "MAPE (%)" = "mape",
      "PICP (%)" = "cicov"
   )

>>>>

---
title: Section Three
header-includes:
   - \usepackage{cleveref}
   - \usepackage{booktabs}
   - \usepackage{texalpha}
   - \input{../symbols.tex}
---

@@

```{r overall_results,echo=FALSE,cache=TRUE,results="asis",dependson="load_results"}
res_overall <- eta_talk %>%
   filter(time_until_arrival > 0) %>%
   summarize(
      pf_rmse = sqrt(mean(pf_error^2)),
      pf_mae = mean(abs(pf_error)),
      pf_mape = mean(abs(pf_error / time_until_arrival)) * 100,
      pf_cicov = mean(pf_ci) * 100,
   #   pf_ci_width = mean(pf_upper - pf_lower),
   #   pf_ci_lower = quantile(pf_upper - pf_lower, 0.025),
   #   pf_ci_upper = quantile(pf_upper - pf_lower, 0.975),
      gtfs_rmse = sqrt(mean(gtfs_error^2)),
      gtfs_mae = mean(abs(gtfs_error)),
      gtfs_mape = mean(abs(gtfs_error / time_until_arrival)) * 100
   ) %>%
   pivot_longer(everything(),
      names_to = c("model", ".value"),
      names_pattern = "([a-z]*)_(.*)"
   ) %>%
   mutate(
      model = c("Particle filter", "Schedule-delay")
   ) %>%
   rename(
      " " = "model",
      "RMSE (s)" = "rmse",
      "MAE (s)" = "mae",
      "MAPE (%)" = "mape",
      "PICP (%)" = "cicov"
   )
